---
title: "Creating a AGEPRO model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a AGEPRO model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Creating Uku projection AGEPRO model

The following example is based on a fishing mortality and stock biomass projection for the uku snapper in Hawaii which was used as an example input file for **AGEPRO-GUI**.

The projection was conducted using results from the base-case Stock Synthesis model to evaluate the probable impacts of constant catch quotas on future spawning stock biomass and yield with a time horizon of **2019-2026**. This projection includes **four fishing fleets** with distinct landings quotas, mean weights at age, and fishery selectivities at age as well as using **three recruitment models** with different probabilities of being the future state of nature. The initial condition for the stochastic projection was based on the distribution of estimated initial population size-at-age in the year 2018. A total of **1000 simulations** were run for each of 100 bootstrap replicates to characterize the effects of uncertainty in initial stock size as well as process errors on the distribution of future recruitment, life history, and fishery parameters.

| field            | value |
|------------------|-------|
| yr_start         | 2019  |
| yr_end           | 2026  |
| age_begin        | 1     |
| age_end          | 32    |
| num_pop_sims     | 1000  |
| num_fleets       | 4     |
| num_rec_models   | 3     |
| discards_present | 0     |
| seed             | 300   |

```{r new_model_setup}
library(ageproR)
test <- agepro_model$new(2019, 2026, 1, 32, 1000, 4, 3, 0, 300)
```

### Set Recruitment Model

By default, AGEPRO models will include NULL recruitment (recruitment model number `0`).
