---
title: "Import AGEPRO model data from AGEPRO input file"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import AGEPRO model data from AGEPRO input file}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

***ageproR** is currently incompatible with the supported AGEPRO input file format* (`AGEPRO VERSION 4.0` & `AGEPRO VERSION 4.2`). *The included example AGEPRO input file* (`inst/test-example4.inp`) *, is a partial implementation of **AGEPRO-GUI**'s Hawaii Uku projection AGEPRO example input file, and is NOT compatible with Jon Brodziak's AGEPRO calculation engine. It is used to demonstrate **ageproR's** current implementation.*

## Hawaii Uku Snapper Example Input File

This input file is a fishing mortality and stock biomass projection for the uku snapper in Hawaii. The projection was conducted using results from the base-case Stock Synthesis model to evaluate the probable impacts of constant catch quotas on future spawning stock biomass and yield with a time horizon of 2019-2026. This projection includes four fishing fleets with distinct landings quotas, mean weights at age, and fishery selectivities at age as well as using three recruitment models with different probabilities of being the future state of nature. The initial condition for the stochastic projection was based on the distribution of estimated initial population size-at-age in the year 2018. A total of 1000 simulations were run for each of 100 bootstrap replicates to characterize the effects of uncertainty in initial stock size as well as process errors on the distribution of future recruitment, life history, and fishery parameters.


## Importing Uku projection AGEPRO model data from AGEPRO input file

```{r setup}
library(ageproR)
test <- agepro_inp_model$new()
```

### Loading a AGEPRO Input File:

```{r read_agepro_input_file}
inp_file <- file.path( here::here(), "inst/test-example4.inp" )
test$read_inp(inp_file)
```

### To set (or correct) bootstrap filename

```{r bootstrap}
bsn_file <- file.path( here::here(), "inst/Example1.BSN" )
test$set_bootstrap_filename(bsn_file)
```
