---
title: "Hawaiian Uku Projection AGEPRO model Example"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Intro 

This vignette will guide you to through the basic functionality of **ageproR**.



# Uku projection AGEPRO model

The following example is based on a fishing mortality and stock biomass projection for the uku snapper in Hawaii. These projections use actual fishery data but are for the purposes for demonstration only.

The projection was conducted using results from the base-case Stock Synthesis model to evaluate the probable impacts of constant catch quotas on future spawning stock biomass and yield with a time horizon of **2019-2026**. This projection includes **four fishing fleets** with distinct landings quotas, mean weights at age, and fishery selectivities at age as well as using **three recruitment models** with different probabilities of being the future state of nature. The initial condition for the stochastic projection was based on the distribution of estimated initial population size-at-age in the year 2018. A total of **1000 simulations** were run for each of 100 bootstrap replicates to characterize the effects of uncertainty in initial stock size as well as process errors on the distribution of future recruitment, life history, and fishery parameters.

# Creating new AGEPRO Model based on Hawaiian Uku Projections 

| field            | value |
|------------------|-------|
| yr_start         | 2019  |
| yr_end           | 2026  |
| age_begin        | 1     |
| age_end          | 32    |
| num_pop_sims     | 1000  |
| num_fleets       | 4     |
| num_rec_models   | 3     |
| discards_present | 0     |
| seed             | 300   |

```{r new_model_setup}
library(ageproR)
test <- agepro_model$new(2019, 2026, 1, 32, 1000, 4, 3, 0, 300)
```

## Set Recruitment Model

By default, AGEPRO models will include NULL recruitment (recruitment model number `0`).

The following recruitment models 

0.  NULL Recruitment.  
3.  Empirical Recruitment Distribution
4.  Two-Stage Empirical Recruits Per Spawning Biomass Distribution
5.  Beverton-Holt Curve with Lognormal Error
6.  Ricker Curve with Lognormal Error
7.  Shepherd Curve with Lognormal Error
14. Empirical Cumulative Distribution Function of Recruitment
15. Two-Stage Empirical Cumulative Distribution Function of Recruitment


Setup recruitment multiple recruitment models.  

TODO


# Importing Hawaiian Uku Projections AGEPRO model data from AGEPRO Input File 

***ageproR** is currently incompatible with the supported AGEPRO input file format* (`AGEPRO VERSION 4.0` & `AGEPRO VERSION 4.2`). 

*The included example AGEPRO input file* (`inst/test-example4.inp`) *, is a partial implementation of **AGEPRO-GUI**'s Hawaii Uku projection AGEPRO example input file, which comes from _Stock Assessment of Uku (Aprion virescens) in Hawaii, 2020_ (Nadon et al. 2020). and is NOT compatible with Jon Brodziak's AGEPRO calculation engine. This example is provided to demonstrate **ageproR's** current implementation and features.*


## Importing Uku projection AGEPRO model data from AGEPRO input file

```{r setup}
library(ageproR)
test <- agepro_inp_model$new()
```

### Loading a AGEPRO Input File:

```{r read_agepro_input_file}
inp_file <- file.path( here::here(), "inst/test-example4.inp" )
test$read_inp(inp_file)
```

### To set (or correct) bootstrap filename

```{r bootstrap}
bsn_file <- file.path( here::here(), "inst/Example1.BSN" )
test$set_bootstrap_filename(bsn_file)
```

